---
title: "P8105 HW1"
author: "Dianchen Li"
date: "2025-09-16"
output: github_document
---

```{r setup, include=FALSE}
library(moderndive)
library(tidyverse)
```
```{r load-data}
data("early_january_weather")
```

# Problem 1
## Dataset Summary
This analysis uses the `early_january_weather` dataset. It has **`r nrow(early_january_weather)`** rows and **`r ncol(early_january_weather)`** columns.  
Key variables include the time `time_hour`, air temperature `temp` (°F), and humidity `humid`.  
The **average temperature** is **`r round(mean(early_january_weather$temp, na.rm = TRUE), 1)` °F**.

```{r p1_plot, message=FALSE, warning=FALSE}
p = ggplot(early_january_weather,
           aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(title = "Temperature over time (colored by humidity)",
       x = "Time (hourly)", y = "Temperature (°F)", color = "Humidity") +
  theme_minimal()

p
```

```{r save_plot, message=FALSE, warning=FALSE}
ggsave("p1_scatter.png", plot = p, width = 7, height = 4, dpi = 300)
```

**Brief interpretation.**  
There is a increasing trend with daily oscillations. And also the color shows that the warmer hours are prone to occur with higher humidity. It is not a linear relationship, there are clusters. But, overall, it still shows a poistive relationship between temperature and humidity.

